---
title: "Happiness in Europe"
params:
  varname: "happy"
  chunks_to_run: "all"
author:
  - name: cpub
    url: https://ctzn.pub/happy_temp
    affiliation: the Citizen Science Lab
    affiliation_url: https://ctzn.pub
date: "`r Sys.Date()`"
output: radix::radix_article
---
 


```{r, eval = FALSE}
<style>

d-title ul {
    grid-column: text;
    list-style-type: none;
    padding-inline-start: 0;
  }


d-title ul a:hover {
    text-decoration: underline;
    text-decoration-color: #FF7A21;
}

#tabs3 .ui-widget-header {
background: transparent;
border: none;
border-bottom: 0 solid #c0c0c0 !important;
-moz-border-radius: 0;
-webkit-border-radius: 0;
border-radius: 0;
text-align: center;
}

#tabs3 .ui-tabs-nav .ui-state-active a {
border-bottom: 1px solid #FF7A21 !important;
}
.toc {
  display: flex;
  color: #333;
    background-color: hsla(206, 90%, 20%, 0.03);
  border-left: 3px solid hsla(206, 50%, 20%, 0.8);
  padding: 1em 2em;
  margin-bottom: 1em;
  counter-increment: problem;
}


d-title ul li {
  display: flex;
  flex-flow: row;
}

d-title li {
  margin-bottom: .75em;
}


.chapter {
  font-family: -apple-system, BlinkMacSystemFont, "Segoe UI", Roboto, Oxygen, Ubuntu, Cantarell, "Fira Sans", "Droid Sans", "Helvetica Neue", Arial, sans-serif !important;
  font-size: 0.75rem;
  font-weight: 400;
  color: rgba(0, 0, 0, 0.5);
  margin: 0;
  text-transform: uppercase;
  font-weight: 500;
  margin-right: 2em;
  white-space: nowrap;
}

d-title ul a {
  color: rgba(0, 0, 0, 0.8);
  text-decoration: none;
  border-bottom: none;
  font-size: 0.999999rem;
  line-height: 1.8em;
}

 

</style>
```

```{r}



toc_function<-function(toc){
pacman::p_load(shiny, stringr)
  toc1<- tags$ul( class="toc", style="display: block;",
                  tags$link(rel = "stylesheet",  href="https://onmundo.org/cpub/design/toc_style.css", integrity="sha384-UHRtZLI+pbxtHCWp1t77Bi1L4ZtiqrqD80Kn4Z8NTSRyMA2Fd33n5dQ8lWUE00s/", crossorigin="anonymous" ),
                  
                  tags$link(rel = "stylesheet",  href="https://use.fontawesome.com/releases/v5.6.3/css/all.css", integrity="sha384-UHRtZLI+pbxtHCWp1t77Bi1L4ZtiqrqD80Kn4Z8NTSRyMA2Fd33n5dQ8lWUE00s/", crossorigin="anonymous" ),
                  tags$table(style="width:100%",(lapply( 1:length(toc),function(tocnum){
                    tags$tr(

                      if (!is.na(toc[[tocnum]]["icon"])){tags$td( style="width:20%" , tags$span(class = "chapter",tags$i(class = toc[[tocnum]][['icon']]),
                                                                                                (tags$a(class = "chapter", href = paste0("#",gsub(" ", "-",trimws(
                                                                                                  gsub('^\\.',"", gsub("^\\d+|", "",tolower(toc[[tocnum]]['title'])))))), toc[[tocnum]]['title']))))}
                      else{ tags$td( style="width:20%" , tags$span(class = "chapter", (tags$a(class = "chapter", href = paste0("#",gsub(" ", "-",trimws(
                        gsub('^\\.',"", gsub("^\\d+|", "",tolower(toc[[tocnum]]['title'])))))), toc[[tocnum]]['title']))))},

                      tags$td(tags$a(href = paste0("#",gsub(" ", "-",trimws(
                        gsub('^\\.',"", gsub("^\\d+|", "",tolower(toc[[tocnum]]['title'])))))), toc[[tocnum]]['description']))
                    )
                  }))))



  toc1<- gsub("[\t\n\r\v\f]", "", toc1)
  str_squish(toc1)


}
```

```{r}



toc <- list(
 c(title = "1. Overview", description = "this is the overview of our document"),
 c(title = "2. This 2nd section", icon = "fas fa-bezier-curve", description = "second section covers other stuff"),
 c(title = "2a. Overview again", description = "this is the overview") )
```


```{r, eval = FALSE}

toc_function<-function(toc){

toc1<- tags$ul( class="toc", style="display: block;",
                tags$link(rel = "stylesheet",  href="https://use.fontawesome.com/releases/v5.6.3/css/all.css", integrity="sha384-UHRtZLI+pbxtHCWp1t77Bi1L4ZtiqrqD80Kn4Z8NTSRyMA2Fd33n5dQ8lWUE00s/", crossorigin="anonymous" ),
         tags$table(style="width:100%",(lapply( 1:length(toc),function(tocnum){
               tags$tr(
                      
if (!is.na(toc[[tocnum]]["icon"])){tags$td( style="width:20%" , tags$span(class = "chapter",tags$i(class = toc[[tocnum]][['icon']]), 
                                                                          (tags$a(class = "chapter", href = paste0("#",gsub(" ", "-",trimws(
gsub('^\\.',"", gsub("^\\d+|", "",tolower(toc[[tocnum]]['title'])))))), toc[[tocnum]]['title']))))}
else{ tags$td( style="width:20%" , tags$span(class = "chapter", (tags$a(class = "chapter", href = paste0("#",gsub(" ", "-",trimws(
gsub('^\\.',"", gsub("^\\d+|", "",tolower(toc[[tocnum]]['title'])))))), toc[[tocnum]]['title']))))},

               tags$td(tags$a(href = paste0("#",gsub(" ", "-",trimws(
gsub('^\\.',"", gsub("^\\d+|", "",tolower(toc[[tocnum]]['title'])))))), toc[[tocnum]]['description']))
)
         }))))
    


toc1<- gsub("[\t\n\r\v\f]", "", toc1)
str_squish(toc1)


}




```


---
description: |
  This file provides template for variable "happy" in ESS. `r  toc_function(toc)`
---


## 1. Overview



'/Applications/RStudio 2.app/Contents/MacOS/pandoc/pandoc' +RTS -K512m -RTS remove_styling.utf8.md --to html5 --from markdown+autolink_bare_uris+ascii_identifiers+tex_math_single_backslash --output remove_styling.html --email-obfuscation none --self-contained --standalone --no-highlight --template /Library/Frameworks/R.framework/Verinclude-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0220dd9e9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a06b7083b9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a054d828ehtml --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a029eed042html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a03e382831html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a042a563fchtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a048debe0dhtml --include-after-body 
 markdown+autolink_bare_uris+ascii_identifiers+tex_math_single_backslash --output remove_styling.html --email-obfuscation none --self-contained --standalone --no-highlight --template /Li
 
R.framework/Versions/3.5/Resources/library/radix/rmarkdown/templates/radix_article/resources/distill.lua '--metadata=link-citations:true' --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a01809a3chtml --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a05396cf27html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0220dd9e9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a06b7083b9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a054d828ehtml --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a029eed042html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a03e382831html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a042a563fchtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a048debe0dhtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a05eda7469html --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0c1e2cb9html --include-in-

R.framework/Versions/3.5/Resources/library/radix/rmarkdown/templates/radix_article/resources/distill.lua '--metadata=link-citations:true' --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a01809a3chtml --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a05396cf27html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0220dd9e9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a06b7083b9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a054d828ehtml --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a029eed042html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a03e382831html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a042a563fchtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a048debe0dhtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a05eda7469html --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0c1e2cb9html --include-in-

R.framework/Versions/3.5/Resources/library/radix/rmarkdown/templates/radix_article/resources/distill.lua '--metadata=link-citations:true' --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a01809a3chtml --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a05396cf27html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0220dd9e9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a06b7083b9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a054d828ehtml --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a029eed042html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a03e382831html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a042a563fchtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a048debe0dhtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a05eda7469html --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0c1e2cb9html --include-in-

 
 
## 2. This 2nd section


R.framework/Versions/3.5/Resources/library/radix/rmarkdown/templates/radix_article/resources/distill.lua '--metadata=link-citations:true' --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a01809a3chtml --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a05396cf27html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0220dd9e9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a06b7083b9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a054d828ehtml --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a029eed042html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a03e382831html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a042a563fchtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a048debe0dhtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a05eda7469html --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0c1e2cb9html --include-in-

R.framework/Versions/3.5/Resources/library/radix/rmarkdown/templates/radix_article/resources/distill.lua '--metadata=link-citations:true' --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a01809a3chtml --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a05396cf27html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0220dd9e9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a06b7083b9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a054d828ehtml --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a029eed042html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a03e382831html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a042a563fchtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a048debe0dhtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a05eda7469html --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0c1e2cb9html --include-in-

R.framework/Versions/3.5/Resources/library/radix/rmarkdown/templates/radix_article/resources/distill.lua '--metadata=link-citations:true' --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a01809a3chtml --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a05396cf27html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0220dd9e9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a06b7083b9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a054d828ehtml --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a029eed042html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a03e382831html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a042a563fchtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a048debe0dhtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a05eda7469html --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0c1e2cb9html --include-in-


## 2a. Overview again


R.framework/Versions/3.5/Resources/library/radix/rmarkdown/templates/radix_article/resources/distill.lua '--metadata=link-citations:true' --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a01809a3chtml --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a05396cf27html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0220dd9e9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a06b7083b9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a054d828ehtml --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a029eed042html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a03e382831html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a042a563fchtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a048debe0dhtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a05eda7469html --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0c1e2cb9html --include-in-

R.framework/Versions/3.5/Resources/library/radix/rmarkdown/templates/radix_article/resources/distill.lua '--metadata=link-citations:true' --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a01809a3chtml --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a05396cf27html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0220dd9e9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a06b7083b9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a054d828ehtml --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a029eed042html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a03e382831html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a042a563fchtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a048debe0dhtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a05eda7469html --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0c1e2cb9html --include-in-

R.framework/Versions/3.5/Resources/library/radix/rmarkdown/templates/radix_article/resources/distill.lua '--metadata=link-citations:true' --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a01809a3chtml --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a05396cf27html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0220dd9e9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a06b7083b9html --include-in-header /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a054d828ehtml --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a029eed042html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a03e382831html --include-before-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a042a563fchtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a048debe0dhtml --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a05eda7469html --include-after-body /var/folders/4j/7zjlsp950nzdf7y7qcxt37200000gn/T//RtmpyCo9iW/file120a0c1e2cb9html --include-in-
